### 2017-11-23 Risk analysis/Text/Layout/Layout/chapter2_methods.tex
correction of important errors

	        \subsection{Abstract valuation of the 1D geological model}\label{sec:1D_score_system}
	        For valuating a simplified 1D model, $OOIP$ and recoverable volume calculations are not applicable, as these require a 3D setting. Given only layer boundary positions in one vertical dimension, it is resorted to an abstract way of reservoir valuation by defining a scoring system. A dimensionless reservoir score is made dependent on three uncertain parameters which can be deduced from the 1D interface positions: (1) reservoir thickness, (2) reservoir top depth and (3) seal thickness (see Figure \ref{fig:3_parameters}).

	        \begin{figure}[h]
	        	\centering
	        	\includegraphics[width=1\textwidth]{Figures/3_parameters.png}
	        	\caption{Probability distributions for the three parameters deduced from the 1D model depicted in Figure \ref{fig:1D_model}. Values from these parameter distributions are combined in Equation \ref{eq:1D_score_system} to attain a score for valuation of reservoir model realizations.}\label{fig:3_parameters}
	        \end{figure}

	        Assuming that reservoir thickness is a simplified indicator for the amount of extractable oil or gas and thus value in place, a gain in score can be correlated with increase in thickness. Here, two score points are assigned to one meter of thickness. Increasing costs of drilling are indicated by increasing depth of the reservoir top. Consequently, one negative score point is ascribed to every meter in depth. Samples from the probability distributions of these two parameters are drawn to model the true score of the reservoir (depth scores are subtracted from reservoir thickness scores).
	        A third parameter is defined by the seal thickness. Score points are not added or subtracted by this parameter directly. Instead, a threshold for seal reliability is defined beforehand. Here, it is set to 20 m thickness. If the seal thickness falls below this threshold, it is assumed that the seal fails completely and thus all the potential value (positive score) of the reservoir is lost, while costs of depth (negative score) remain. Thus, a condition to check whether the seal is reliable is included in the model. A respective equation for the reservoir score $S_{res}$ is defined as:

@@

			where reservoir thickness is given by $h_{res}$, seal thickness by $h_{seal}$ and reservoir depth, which is always a negative value, by $d_{res}$.\\
			This valuation method is applied on the original prior-only Monte Carlo sampling of the 1D model as reference and then on each posterior distribution set after conducting Bayesian inference. Resulting score probability distributions can be compared directly and additionally under use of the case-specific custom loss function (Equation \ref{eq:LFR_final}) defined before.

>>>>

	        \subsection{Abstract valuation of the 1D geological model}\label{sec:1D_score_system}
	        For valuating a simplified 1D model, $OOIP$ and recoverable volume calculations are not applicable, as these require a 3D setting. Given only layer boundary positions in one vertical dimension, it is resorted to an abstract way of reservoir valuation by defining a scoring system. A dimensionless reservoir score is made dependent on three derivatives of the uncertain 1D interface positions: (1) reservoir thickness, (2) reservoir top depth and (3) seal thickness. From these, (2) equals the prior parameter that indicates the reservoir-seal boundary in depth. The other two are respectively deduced from the distance between parameter values. According to this dependence, these values, which we use to valuate the reservoir, inherit the uncertainty from their parent parameters. An exemplary comparison between the distribution of these values depending on prior and posterior parameters is depicted in Figure \ref{fig:3_parameters}. We hereby illustrate how model uncertainties are translated to uncertainties related to valuation measures.\\
	        \begin{figure}[h]
	        	\centering
	        	\includegraphics[width=1\textwidth]{Figures/3_parameters.png}
	        	\caption{Probability distributions for the three factors used in the abstract reservoir valuation as formulated in Equation \ref{eq:1D_score_system}. These are deduced from the 1D model input parameters and are thus uncertain. Here, we show factors deduced from prior parameters in Figure \ref{fig:1D_model} and factors resulting from exemplary posterior parameter distributions.}\label{fig:3_parameters}
	        \end{figure}
	        Assuming that reservoir thickness is a simplified indicator for the amount of extractable oil or gas and thus value in place, a gain in score can be correlated with increase in thickness. Here, two score points are assigned to one meter of thickness. Increasing costs of drilling are indicated by increasing depth of the reservoir top. Consequently, one negative score point is ascribed to every meter in depth. Samples from the probability distributions of these two parameters are drawn to model the true score of the reservoir (depth scores are subtracted from reservoir thickness scores).
	        A third parameter is defined by the seal thickness. Score points are not added or subtracted by this parameter directly. Instead, a threshold for seal reliability is defined beforehand. Here, it is set to 20 m thickness. If the seal thickness falls below this threshold, it is assumed that the seal fails completely and thus all the potential value (positive score) of the reservoir is lost, while costs of depth (negative score) remain. Thus, a condition to check whether the seal is reliable is included in the model. A respective equation for the reservoir score $S_{res}$ is defined as:

@@

			where reservoir thickness is given by $h_{res}$, seal thickness by $h_{seal}$ and reservoir depth, which is always a negative value, by $d_{res}$.\\
			This valuation method is applied on the original prior-only Monte Carlo simulation of the 1D model as reference and then on each posterior distribution set after conducting Bayesian inference. Resulting score probability distributions can be compared directly and additionally under use of the case-specific custom loss function (Equation \ref{eq:LFR_final}) defined before.

### 2017-11-23 Risk analysis/Text/Layout/Layout/chapter3_results.tex
Enough for today
correction of important errors

			Full scoring results, including also seal reliability (with a threshold of 20~m) as a parameter, are visualized in Figure \ref{fig:score_results1} (B). The main distribution is not changed significantly, except for a striking peak of probability at the possibility for a score of -2000. This presumably represents the bulk of cases, in which the seal is assumed to have failed. Regarding this, it is to be noted, that the mean of the seal top distribution is found at -2000 m. It can be seen in Figure \ref{fig:update_moderate1} (A1), that around that depth in the model column, reservoir top and seal top probability distributions significantly overlap. Thus, there is a possibility for a higher score, due to a shallower reservoir top position, but also a high probability for a seal thickness below the safety cut-off threshold of 20~m. The negative score peak at -2000 is thus presumably caused by a high number of seal failures, due to both layer interfaces located within this range. Furthermore, as a consequence of this negative peak, mean and median of the score distribution have been shifted to lower values and are now found further apart (see Figure \ref{fig:score_results1} (B)).\\

@@

		\subsection{Posterior model IV: SSF likelihood reinforcing trap reliability}%ML4
		For this fourth model, thickness likelihoods were chosen to be comparable to those of model I, i.e. supporting the probability of thick layers in general. Additionally, a $SSF$-related likelihood function was implemented. With a mean of 1.5 and a standard deviation of 0.5, it was chosen to mostly reinforce the likelihood of a $SSF$ below the critical value of $SSF_c = 3$.\\
		In Figure \ref{ML4} (b), it can be seen that the uncertainty about the position of interfaces in the footwall was greatly reduced for all layers. In the hanging wall, information entropy remained high but was shifted upwards and mainly concentrated in an area that is juxtaposed to the footwall seal formation.\\
		In the resulting $ROV$ distribution, the possibility of trap failure was completely extinguished, while the probability of high volumes in the range between 3.5  and 5 million m$^3$ was significantly increased. Mean and median are found at almost the same value, but the bulk of the distribution found in this range appears to be slightly bimodal in itself, resembling approximately the shape of two normal distributions overlapping around the value of 4 million m$^3$.\\
		Accordingly, Bayes actions converged within this range of positive values. Considering the two modes in this range, risk-averse to risk-neutral bids remained in the middle of the mode of lower volumes, while risk-friendly actors were encouraged to estimate higher volumes as found in the second mode. Overall, significant convergence was achieved, also in respect to expected losses.\\		
		The importance of a reliable seal is once again emphasized by these results. Reliable fault sealing was favored by the chosen $SSF$ likelihood. It should be pointed out that computation of the complete model is required to attain the $SSF$. This value is furthermore characterized by a complex interdependence with other parameters and is most directly related to layer thicknesses and fault offset. For this reason, information entropy and offset uncertainty in the hanging wall were not greatly reduced. However, the certainty about the ratio of displacement to layer thicknesses was presumably improved by using the $SSF$ in a likelihood function.

>>>>

			Full scoring results, including also seal reliability (with a threshold of 20~m) as a parameter, are visualized in Figure \ref{fig:score_results1} (B). The main distribution is not changed significantly, except for a striking peak of probability at the possibility for a score of -2000. This presumably represents the bulk of cases in which the seal is assumed to have failed. Regarding this, it is to be noted, that the mean of the seal top distribution is found at -2000 m. It can be seen in Figure \ref{fig:update_moderate1} (A1), that around that depth in the model column, reservoir top and seal top probability distributions significantly overlap. Thus, there is a possibility for a higher score, due to a shallower reservoir top position, but also a high probability for a seal thickness below the safety cut-off threshold of 20~m. The negative score peak at -2000 is thus presumably caused by a high number of seal failures, due to both layer interfaces located within this range. Furthermore, as a consequence of this negative peak, mean and median of the score distribution have been shifted to lower values and are now found further apart (see Figure \ref{fig:score_results1} (B)).\\

@@

		\subsection{Posterior model IV: SSF likelihood reinforcing trap reliability}%ML4
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/Appendix/ML4}
			\caption{....}\label{fig:ML4}
		\end{figure}
		For this fourth model, thickness likelihoods were chosen to be comparable to those of model I, i.e. supporting the probability of thick layers in general. Additionally, a $SSF$-related likelihood function was implemented. With a mean of 1.5 and a standard deviation of 0.5, it was chosen to mostly reinforce the likelihood of a $SSF$ below the critical value of $SSF_c = 3$.\\
		In Figure \ref{fig:ML4} (b), it can be seen that the uncertainty about the position of interfaces in the footwall was greatly reduced for all layers. In the hanging wall, information entropy remained high but was shifted upwards and mainly concentrated in an area that is juxtaposed to the footwall seal formation.\\
		In the resulting $ROV$ distribution, the possibility of trap failure was completely extinguished, while the probability of high volumes in the range between 3.5  and 5 million m$^3$ was significantly increased. Mean and median are found at almost the same value, but the bulk of the distribution found in this range appears to be slightly bimodal in itself, resembling approximately the shape of two normal distributions overlapping around the value of 4 million m$^3$.\\
		Accordingly, Bayes actions converged within this range of positive values. Considering the two modes in this range, risk-averse to risk-neutral bids remained in the middle of the mode of lower volumes, while risk-friendly actors were encouraged to estimate higher volumes as found in the second mode. Overall, significant convergence was achieved, also in respect to expected losses.\\		
		The importance of a reliable seal is once again emphasized by these results. Reliable fault sealing was favored by the chosen $SSF$ likelihood. It should be pointed out that computation of the complete model is required to attain the $SSF$. This value is furthermore characterized by a complex interdependence with other parameters and is most directly related to layer thicknesses and fault offset. For this reason, information entropy and offset uncertainty in the hanging wall were not greatly reduced. However, the certainty about the ratio of displacement to layer thicknesses was presumably improved by using the $SSF$ in a likelihood function.
